\setlength{\footskip}{8mm}

\chapter{Conclusion and Recommendations}
\label{ch:conclusion}

\textit{We summarize the contributions of the dissertation and
provide recommendations for further work.}

\section{Conclusion}

In this dissertation, we have proposed and evaluated a new method for
bootstrapping scene-specific anomalous human behavior detection systems that
incrementally learns behavior models without requiring storage of large
databases of training data. The method requires minimal involvement of a human
operator; the only required action is to label the patterns in a small
bootstrap set as normal or anomalous and then to label false positive alarms as
normal when they occur.

Our contributions are five-fold. First, we have developed a blob extraction and
appearance-based blob tracking method (explained in
Chapter~\ref{ch:blobanalysis}) that segments blobs and generate blobs'
trajectories as input to the behavior modeling module. Although the method
works well with typical surveillance data, the blob tracking method is not
always robust for complex events involving multiple people. 

Second, we propose a new method for detecting shadows using a simple maximum
likelihood approach based on color information (explained in
Chapter~\ref{ch:shadow}). We extend the deterministic nonmodel-based approach,
designing a parametric statistical model-based approach.  In our experiments,
we find that our method works well in many cases but misclassifies shadow
pixels in regions that have similar color to the background.  

Third, we propose and evaluate a new method for clustering human behaviors
(explained in Chapter~\ref{ch:clustering}). The method can be used to bootstrap
an anomaly detection module for intelligent video surveillance systems. The
combination of DTW with the type of linear HMMs we use in this work is
extremely effective in separating anomalous from typical behaviors on
real-world testbed video surveillance data. One main limitation of this work is
that the method creates a large number of single-sequence clusters that would
have to be manually labeled as normal or abnormal by security personnel.

Fourth, we propose a \textit{semi-supervised} method for automatic
identification of suspicious behavior from a small bootstrap set (explained in
Chapter~\ref{ch:batch}). The method partitions the bootstrap set into clusters
then assigns new observation sequences to clusters based on statistical tests
of HMM log likelihood scores.  Our experiments find that the size of the
bootstrap set could affect the results of the current system.  With more
bootstrap data we tend to discover more compact behavior classes, leading to
better anomaly detection rates in practice. The main limitation of the method
proposed in this chapter is that it never learns any new typical behavior over
time. This requires a more adaptive approach to learn new behaviors over time.
We address this issue in the next contribution. 

Fifth, we propose an incremental behavior modeling and suspicious activity
detection method (explained in Chapter~\ref{ch:incremental}) that incrementally
learns scene-specific statistical models of human behavior without requiring
storage of large databases of training data.

The experimental results presented in this dissertation are extremely
promising, demonstrating that our approach is a practical and effective
solution to the problem of inducing scene-specific statistical models useful
for bringing suspicious behavior to the attention of human security personnel.
Deploying our system on a large video sensor network would potentially lead to
substantial increases in the productivity and proactivity of human monitors.

That said, as mentioned above, the work has several limitations that could be
addressed with further research. Next, I provide recommendations for future
research.

\section{Recommendations}

Our approach can be extended to larger-scale situations as long as typical
behavior can be modeled in terms of the spatio-temporal motion of foreground
blobs.  It could also be extended to recognize more complex events involving
multiple persons --- we believe that we can handle interactions between
pedestrians, for example in pickpocket and assault events, within the current
framework of temporal statistical models for individual humans by including
observation features that characterize a person's interaction with others while
in the scene.  Integrating with pedestrian detection and tracking methods that
rely on body part detection and tracking rather than motion blob tracking might
help capture a larger proportion of the kinds of unusual behaviors we would
observe in building entrances or office hallways.

Although the current method would work well for most building entrances, office
building hallways, and similar environments, the blob tracking process would
not be robust for scenes with dense crowds. Integrating with pedestrian
tracking methods for crowds \shortcite{ali12crowds} would be a potential
solution to the problem.

In some cases, our shadow detection method misdetects shadow pixels as object
pixels due to similar colors between the object and the background and unclear
background texture in shadow regions. Incorporating geometric or shadow region
shape priors would potentially improve detection and discrimination rates.

Next, constructing a fixed codebook to quantize the feature space may be
inappropriate for incremental approaches since the codebook would need to be
revised over time to account for changing ``typical'' behaviors.  It may be
better to take a probabilistic generative approach to the assignment of feature
vectors to discrete categories rather than making hard assignments.

We found in the experiments that our clustering method tends to construct
unbalanced dendrogram structures that leads our method to create a large number
of single-sequence clusters. An approach to maintain the balanced dendrogram
structure could address this issue. 

Also, our current system can add new HMMs but cannot remove them. Over time,
the number of HMMs would grow without bound.  It would be better to
periodically merge similar models or remove old models that no longer represent
typical behavior. Since each HMM has the same structure, it would be very
straightforward to check for pairs of similar models and merge them.

The clustering results suggest it is likely that the patterns DTW groups
together are perfectly suited for modeling by linear HMMs with bypass
transitions. We may further explore this idea in future work.

In the experimental results for our incremental method, we have shown that
local event processing is more effective than global event processing on our
data set.  It would be interesting to compare to a hybrid approach in which we
apply the global method to blocks in an image rather than the whole image.  

Lastly, we will explore integrating the behavior understanding and anomaly
detection algorithms into a complete video surveillance system such as
ZoneMinder \shortcite{zoneminder}.

\FloatBarrier

