%==========================================================
%======================  FRONT STUFF ======================
%==========================================================

%======================= Cover Page =======================
%\begin{document}
\newpage
\DIFdelbegin %DIFDELCMD < \pagestyle{plain}
%DIFDELCMD < \pagenumbering{roman}
%DIFDELCMD < \setcounter{page}{1}
%DIFDELCMD < %%%
\DIFdelend \DIFaddbegin 

%DIF >  Set this page style from plain to empty, so the page number 
%DIF >  will not be put on this page.
\pagestyle{empty}

%DIF > \pagenumbering{roman}
%DIF > \setcounter{page}{1}

\DIFaddend \addcontentsline{toc}{section}{Title Page}
%\setlength{\footskip}{-15mm}
\setlength{\textheight}{230mm}
\setlength{\voffset}{10mm}
\vskip -5em

\begin{center}
{ 
%DIF >     \singlespace \uppercase{\bf Incremental Behavior Modeling and
%DIF >     Suspicious Activity Detection} \par
    \singlespace \DIFdelbegin %DIFDELCMD < \uppercase{\bf Incremental Behavior Modeling and
%DIFDELCMD <     Suspicious Activity Detection} %%%
\DIFdelend \DIFaddbegin {\large \bf \DIFadd{Incremental Behavior Modeling and
    Suspicious Activity Detection}} \DIFaddend \par
}
\vskip 2em
{
    \lineskip 1.5em
    \begin{tabular}[t]{c} by\\ \\ Kan Ouivirach
    \end{tabular}\par
}
%\vskip 5.6em

\vskip 3.5em
\singlespace A dissertation submitted in partial fulfillment of the
requirements for the\\ degree of Doctor of Philosophy in\\ Computer
Science

%DIF < 	\vskip 5em
%DIF > \vskip 5em
\vskip 0.5em
{
    \singlespace
    \begin{center}
        \begin{tabular}{rl}
        \\[-1em]
        Examination Committee: & Dr.\ Matthew N.\ Dailey (Chairperson) \\[-0.8em]
                               & Dr.\ Nitin V.\ Afzulpurkar \\[-0.8em]
                               & Dr.\ Supavadee Aramvith \DIFaddbegin \DIFadd{(External Expert) }\DIFaddend \\[-0.8em]
                               & Dr.\ Sanparith Marukatat \DIFaddbegin \DIFadd{(External Expert) }\DIFaddend \\\\

        External Examiner:     & Prof.\ James J.\ Clark \\[-0.8em]
                               & Dept.\ of Electrical and Computer Engineering \\[-0.8em]
                               & McGill University, Canada \\\\

        Nationality:     & Thai \\[-0.8em]
        Previous Degree: & Master of Engineering in Computer Science\\[-0.8em]
                         & Asian Institute of Technology, Thailand\\[-0.8em]
        \\
        Scholarship Donor: & Royal Thai Government \DIFaddbegin \DIFadd{Fellowship }\DIFaddend \\[-0.8em]
        \\
        \end{tabular}
    \end{center}

    \vskip 3.0em
    \centerline{}
    \vskip 2em
}
\end{center}
\begin{center}
    \singlespace Asian Institute of Technology\\ School of Engineering
                  and Technology\\ Thailand\\ \DIFdelbegin \DIFdel{May }\DIFdelend \DIFaddbegin \DIFadd{December }\DIFaddend 2013
\end{center}
\vfill

%====================== ACKNOWLEDGEMENTS ======================
\newpage
\DIFaddbegin 

\DIFaddend \pagestyle{plain}
\DIFaddbegin 

%DIF >  Maybe these two commands below are not necessary.
\pagenumbering{roman}
\setcounter{page}{2}

\DIFaddend \addcontentsline{toc}{section}{Acknowledgments}
\onecolumn % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.
\setlength{\footskip}{8mm}
\begin{center}
{
    \large \bf Acknowledgments\\ \vskip 1em
}
\vskip 1em
\end{center}
\singlespace
\doublespace
\hspace{8.5mm}
\vspace{-1em}

My research work was accomplished through the support of many
people. I would like to thank all of them here.

First, my deepest thanks and a special word of appreciation go to 
my beloved parents, who always inspire and give me endless unconditional 
love and support. I dedicate this piece of work to them.

Second, I would like to express my sincere thanks to my advisor, 
Dr.\ Matthew N.\ Dailey, for giving me invaluable advice, excellent 
guidance, strong encouragement and support throughout the study with his
kindness and cordial attitude. I also thank him for being very patient
with me and always willingly answering all my questions.

Third, I would like to extend my sincere gratitude to my committee 
members, Dr.\ Nitin V.\ Afzulpurkar, Dr.\ Supavadee Aramvith, 
and Dr.\ Sanparith Marukatat, for their valuable suggestions
and constructive criticism.

Fourth, I would like to thank the Royal Thai Government for their 
graduate scholarship throughout my studies at AIT. Without the 
scholarship, studying at AIT would be impossible.

\DIFaddbegin \DIFadd{Fifth, I would like to thank Prof.}\ \DIFadd{James J.}\ \DIFadd{Clark for the careful 
review and constructive comments. 
}

\DIFaddend Finally, I am very grateful to have been a part of the AIT Vision and 
Graphics Lab (VGL). I am thankful to all of the lab members for 
valuable discussions and comments on this work. Special thanks are 
due to Shashi Gharti, who assisted with the implementation of human 
tracking and feature extraction, and Phattanapon Rhienmora, who has 
been encouraging and supporting me during my Ph.D.\ life.

%====================== PUBLICATIONS ======================


%====================== ABSTRACT ======================
\newpage
\pagestyle{plain}
\addcontentsline{toc}{section}{Abstract}
\onecolumn % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.

\setlength{\footskip}{8mm}

\begin{center}
{\large \bf Abstract \\ \vskip 1em}
\vskip 1em
\end{center}
\singlespace
\doublespace
\hspace{8.5mm}
\vspace{-1em}

Video surveillance systems have become widespread tools for monitoring
and law enforcement in public areas.  Due to increasing crime, video
surveillance systems are being deployed in more and more places.
Video surveillance systems are needed to help security personnel
prevent and respond to criminal activity in a timely fashion.
However, human monitoring becomes increasingly expensive and
ineffective as the amount of video data increases. Also, manual review of
all video footage is time-intensive and error-prone.

Automated anomaly detection can help to improve the effectiveness of
human observers by separating the video stream into a sequence of
``normal'' and ``unusual'' events. However, much of the existing work
has many limitations in this direction. Oftentimes, separate models
for each distinct a priori known class of ``normal'' behavior are
assumed.  This could lead to the problem of typical behavior evolving
and becoming more diverse to the point that the false alarm rates
increase.  The naive solution would be to retain all of the
observation data and retrain the system periodically, but this
requires storing all of the incoming data, requiring too much disk
space. In this dissertation, we therefore propose and evaluate an
efficient method for incremental automatic identification of
suspicious behavior in video surveillance data.

First, we develop a blob extraction method that segments blobs and an
appearance-based blob tracking method that uses a forward-backward
overlap method and color coherence vectors (CCVs) to maintain identity
through blob merging and splitting cases.

Second, we propose a new method for detecting shadows using a simple
maximum likelihood formulation based on HSV color information. We find
that the method outperforms standard shadow detection methods on three
different real-world video surveillance data sets.

Third, we propose a new method for clustering human behaviors in the
context of video surveillance that is suitable for bootstrapping an
anomaly detection module for intelligent video surveillance
systems. We show that the method is extremely effective in separating
anomalous from typical behaviors on real-world testbed video
surveillance data.

Fourth, we propose a \textit{semi-supervised} batch anomaly
detection method that self-calibrates itself from a small bootstrap
set in which each bootstrap sequence is manually labeled as normal or
suspicious by a human operator. Our method proves extremely effective,
with a very low false alarm rate at a 100\% hit rate.

Finally, we propose an effective behavior modeling and suspicious
activity detection method extending the batch method that
incrementally learns scene-specific statistical models of human
behavior without requiring storage of historical data. The incremental
method's false alarm rate drops below that of the batch method on the
same data.

In experimental evaluations on real-world testbed video surveillance
data sets, the proposed methods prove to be practical and effective at
inducing scene-specific statistical models useful for bringing
suspicious behavior to the attention of human security personnel.

\setlength{\parskip}{0pt} 
%======================= Table of Contents =========================
\newpage
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents

% Page 2 begins

%===================== List of Figures ======================
\newpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

%\clearpage     % \clearpage ends the page, and also dumps out all floats.
%\end{document} % Floats are things like tables and figures.

%\clearpage     % \clearpage ends the page, and also dumps out all floats.

% %===================== List of Tables ======================
\newpage
\addcontentsline{toc}{section}{List of Tables}
\listoftables

% %\clearpage     % \clearpage ends the page, and also dumps out all floats.
% %\end{document} % Floats are things like tables and figures.

%\clearpage     % \clearpage ends the page, and also dumps out all floats.

% %===================== List of Symbols ======================
\newpage
\addcontentsline{toc}{section}{List of Symbols}

\begin{center}
    {\large \bf List of Symbols\\ \vskip 1em}
    \vskip 1em
\end{center}
\singlespace

\begin{table}[h]
    \begin{tabular}{lll}
        \DIFdelbeginFL \DIFdelFL{Test }\DIFdelendFL \DIFaddbeginFL \DIFaddFL{$\vec{f}_i^t$ }\DIFaddendFL & & \DIFdelbeginFL \DIFdelFL{This is a test}\DIFdelendFL \DIFaddbeginFL \DIFaddFL{Feature vector of track $i$ at time $t$}\DIFaddendFL . \\
        \DIFdelbeginFL \DIFdelFL{What }\DIFdelendFL \DIFaddbeginFL \DIFaddFL{$V$ }\DIFaddendFL & & \DIFdelbeginFL \DIFdelFL{This is a what. }\DIFdelendFL \DIFaddbeginFL \DIFaddFL{Set of discrete categories (cluster IDs). }\\
        \DIFaddFL{$U$ }& & \DIFaddFL{Number of categories.  }\\
        \DIFaddFL{$\Theta$ }& & \DIFaddFL{Model estimate for shadows. }\\ 
        \DIFaddFL{$sh$ }& & \DIFaddFL{Shadow. }\\
        \DIFaddFL{$obj$ }& & \DIFaddFL{Object. }\\
        \DIFaddFL{$L_i$ }& & \DIFaddFL{Log of the probability of a sequence $O_i$ given the HMM $M_c$. }\\
        \DIFaddFL{$\vec{O_i}$ }& & \DIFaddFL{Observation sequence $i$. }\\
        \DIFaddFL{$T_i$ }& & \DIFaddFL{Number of observations in sequence $i$. }\\
        \DIFaddFL{$M_c$ }& & \DIFaddFL{HMM that models the sequences in cluster $c$. }\\
        \DIFaddFL{$p_c$ }& & \DIFaddFL{Optimal rejection threshold for cluster $c$. }\\
        \DIFaddFL{$N_c$ }& & \DIFaddFL{Number of deviant patterns allowed in cluster $c$. }\\
        \DIFaddFL{$z$ }& & \DIFaddFL{$z$-value. }\\
        \DIFaddFL{$\theta_z$ }& & \DIFaddFL{Global alarm threshold. }\\

        
    \DIFaddendFL \end{tabular}
\end{table}

% %===================== List of Acronyms ======================
\newpage
\addcontentsline{toc}{section}{List of Acronyms}

\begin{center}
    {\large \bf List of Acronyms\\ \vskip 1em}
    \vskip 1em
\end{center}

\singlespace

\begin{table}[h]
    \begin{tabular}{lll}
        \DIFaddbeginFL \DIFaddFL{CCTV   }& & \DIFaddFL{Closed-Circuit Television. }\\
        \DIFaddFL{MoG    }& & \DIFaddFL{Mixture of Gaussian. }\\
        \DIFaddFL{CCV    }& & \DIFaddFL{Color Coherence Vector. }\\
        \DIFaddFL{DNM    }& & \DIFaddFL{Deterministic Nonmodel-Based. }\\
        \DIFaddFL{NCC    }& & \DIFaddFL{Normalized Cross-Correlation. }\\
        \DIFaddFL{ML     }& & \DIFaddFL{Maximum Likelihood. }\\
        \DIFaddFL{IML    }& & \DIFaddFL{Incremental Maximum Likelihood. }\\
        \DIFaddFL{EM     }& & \DIFaddFL{Expectation Maximization. }\\  
        \DIFaddFL{DBN    }& & \DIFaddFL{Dynamic Bayesian Network. }\\
        \DIFaddFL{$k$-NN }& & \DIFaddFL{$k$-Nearest Neighbors. }\\
        \DIFaddFL{SVM    }& & \DIFaddFL{Support Vector Machine. }\\
        \DIFaddFL{PCA    }& & \DIFaddFL{Principal Component Analysis. }\\
        \DIFaddFL{MDL    }& & \DIFaddFL{Minimum Description Length. }\\
        \DIFaddFL{GMM    }& & \DIFaddFL{Gaussian Mixture Model. }\\
        \DIFaddendFL HMM    & & Hidden Markov Model. \\
        DTW    & & Dynamic Time Warping. \\ 
        \DIFaddbeginFL \DIFaddFL{LRT    }& & \DIFaddFL{Likelihood Ratio Test. }\\
        \DIFaddendFL ROC    & & Receiver Operating Characteristic. \\
        \DIFaddbeginFL \DIFaddFL{EER    }& & \DIFaddFL{Equal Error Rate.
    }\end{tabular}
\end{table}

\newpage

\begin{table}[h]
    \begin{tabular}{lll}
        \DIFaddendFL TP     & & The number of True Positive. \\ 
        FP     & & The number of False Positive. \\
        TN     & & The number of True Negative. \\ 
        FN     & & The number of False Negative. \\
        TPR    & & True Positive Rate. \\ 
        FPR    & & False Positive Rate. 
    \end{tabular}
\end{table}

\setlength{\parskip}{12pt}

