%==========================================================
%======================  FRONT STUFF ======================
%==========================================================

%======================= Cover Page =======================
%\begin{document}
\newpage

% Set this page style from plain to empty, so the page number 
% will not be put on this page.
\pagestyle{empty}

%\pagenumbering{roman}
%\setcounter{page}{1}

\addcontentsline{toc}{section}{Title Page}
%\setlength{\footskip}{-15mm}
\setlength{\textheight}{230mm}
\setlength{\voffset}{10mm}
\vskip -5em

\begin{center}
{ 
%    \singlespace \uppercase{\bf Incremental Behavior Modeling and
%    Suspicious Activity Detection} \par
    \singlespace {\large \bf Incremental Behavior Modeling and
    Suspicious Activity Detection} \par
}
\vskip 2em
{
    \lineskip 1.5em
    \begin{tabular}[t]{c} by\\ \\ Kan Ouivirach
    \end{tabular}\par
}
%\vskip 5.6em

\vskip 3.5em
\singlespace A dissertation submitted in partial fulfillment of the
requirements for the\\ degree of Doctor of Philosophy in\\ Computer
Science

%\vskip 5em
\vskip 0.5em
{
    \singlespace
    \begin{center}
        \begin{tabular}{rl}
        \\[-1em]
        Examination Committee: & Dr.\ Matthew N.\ Dailey (Chairperson) \\[-0.8em]
                               & Dr.\ Nitin V.\ Afzulpurkar \\[-0.8em]
                               & Dr.\ Supavadee Aramvith (External Expert) \\[-0.8em]
                               & Dr.\ Sanparith Marukatat (External Expert) \\\\

        External Examiner:     & Prof.\ James J.\ Clark \\[-0.8em]
                               & Dept.\ of Electrical and Computer Engineering \\[-0.8em]
                               & McGill University, Canada \\\\
		
        Nationality:     & Thai \\[-0.8em]
        Previous Degree: & Master of Engineering in Computer Science\\[-0.8em]
                         & Asian Institute of Technology, Thailand\\[-0.8em]
        \\
        Scholarship Donor: & Royal Thai Government Fellowship \\[-0.8em]
        \\
        \end{tabular}
    \end{center}

    \vskip 3.0em
    \centerline{}
    \vskip 2em
}
\end{center}
\begin{center}
    \singlespace Asian Institute of Technology\\ School of Engineering
                  and Technology\\ Thailand\\ December 2013
\end{center}
\vfill

%====================== DEDICATED PAGE ========================
\newpage

\pagestyle{empty}

\begin{center}
\vspace*{\fill}
This dissertation is dedicated to my parents. 
\vspace*{\fill}
\end{center}

%====================== ACKNOWLEDGEMENTS ======================
\newpage

\pagestyle{plain}

% Maybe these two commands below are not necessary.
\pagenumbering{roman}
\setcounter{page}{3}

\addcontentsline{toc}{section}{Acknowledgments}
\onecolumn % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.
\setlength{\footskip}{8mm}
\begin{center}
{
    \large \bf Acknowledgments\\ \vskip 1em
}
\vskip 1em
\end{center}
\singlespace
\doublespace
\hspace{8.5mm}
\vspace{-1em}

This research work was accomplished through the support of many people. My most
humble and sincere thanks to:

As always, first and foremost, my beloved parents, who inspire me and offer
endless unconditional love and support. My deepest thanks and heartfelt
appreciation cannot go to anyone else but them.

My tireless and trusted advisor, Dr.\ Matthew N.\ Dailey, for giving me
invaluable advice, excellent guidance, strong encouragement, and support
throughout my work with unbridled kindness and support. I also thank him for
being very patient with me and always willingly answering all my questions. 

My committee members, Dr.\ Nitin V.\ Afzulpurkar, Dr.\ Supavadee Aramvith, and
Dr.\ Sanparith Marukatat, for their valuable insight, suggestions and
constructive criticism. 

My external examiner, Prof.\ James J.\ Clark, for his meticulous review and
constructive commentary. 

All of my friends at the AIT Vision and Graphics Lab (VGL) for enthusiastic
discussions and comments on this work. In particular, Shashi Gharti, who
conducted extensive research in areas related to the implementation of human
tracking and feature extraction, and Phattanapon Rhienmora, who has been
encouraging and supportive during the time I spent in pursuit of my Ph.D., and
even to this day. I am eternally grateful to have been a part of this lab.

CSIM secretaries, Ms.\ Pintip Thavornchan, Ms.\ Sireekant Thanwongpan, and Ms.\
Siriporn Nanthasing, for their irreplaceable assistance during my studies, and
without whom all things descend into chaos.

AITians for healthy conversations and their true friendship while I was living
on campus at AIT.

Last but not least, the Royal Thai Government for the graduate scholarship that
facilitated my studies at AIT. Without the scholarship, my studies at AIT would
have been impossible.  

%====================== ABSTRACT ======================
\newpage
\pagestyle{plain}
\addcontentsline{toc}{section}{Abstract}
\onecolumn % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.

\setlength{\footskip}{8mm}

\begin{center}
{\large \bf Abstract \\ \vskip 1em}
\vskip 1em
\end{center}
\singlespace
\doublespace
\hspace{8.5mm}
\vspace{-1em}

Video surveillance systems have become widespread tools for monitoring
and law enforcement in public areas.  Due to increasing crime, video
surveillance systems are being deployed in more and more places.
Video surveillance systems are needed to help security personnel
prevent and respond to criminal activity in a timely fashion.
However, human monitoring becomes increasingly expensive and
ineffective as the amount of video data increases. Also, manual review of
all video footage is time-intensive and error-prone.

Automated anomaly detection can help to improve the effectiveness of
human observers by separating the video stream into a sequence of
``normal'' and ``unusual'' events. However, much of the existing work
has many limitations in this direction. Oftentimes, separate models
for each distinct a priori known class of ``normal'' behavior are
assumed.  This could lead to the problem of typical behavior evolving
and becoming more diverse to the point that the false alarm rates
increase.  The naive solution would be to retain all of the
observation data and retrain the system periodically, but this
requires storing all of the incoming data, requiring too much disk
space. In this dissertation, we therefore propose and evaluate an
efficient method for incremental automatic identification of
suspicious behavior in video surveillance data.

First, we develop a blob extraction method that segments blobs and an
appearance-based blob tracking method that uses a forward-backward
overlap method and color coherence vectors (CCVs) to maintain identity
through blob merging and splitting cases.

Second, we propose a new method for detecting shadows using a simple
maximum likelihood formulation based on HSV color information. We find
that the method outperforms standard shadow detection methods on three
different real-world video surveillance data sets.

Third, we propose a new method for clustering human behaviors in the
context of video surveillance that is suitable for bootstrapping an
anomaly detection module for intelligent video surveillance
systems. We show that the method is extremely effective in separating
anomalous from typical behaviors on real-world testbed video
surveillance data.

Fourth, we propose a \textit{semi-supervised} batch anomaly
detection method that self-calibrates itself from a small bootstrap
set in which each bootstrap sequence is manually labeled as normal or
suspicious by a human operator. Our method proves extremely effective,
with a very low false alarm rate at a 100\% hit rate.

Finally, we propose an effective behavior modeling and suspicious
activity detection method extending the batch method that
incrementally learns scene-specific statistical models of human
behavior without requiring storage of historical data. The incremental
method's false alarm rate drops below that of the batch method on the
same data.

In experimental evaluations on real-world testbed video surveillance
data sets, the proposed methods prove to be practical and effective at
inducing scene-specific statistical models useful for bringing
suspicious behavior to the attention of human security personnel.

\setlength{\parskip}{0pt} 
%======================= Table of Contents =========================
\newpage
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents

% Page 2 begins

%===================== List of Figures ======================
\newpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

%\clearpage     % \clearpage ends the page, and also dumps out all floats.
%\end{document} % Floats are things like tables and figures.

%\clearpage     % \clearpage ends the page, and also dumps out all floats.

% %===================== List of Tables ======================
\newpage
\addcontentsline{toc}{section}{List of Tables}
\listoftables

% %\clearpage     % \clearpage ends the page, and also dumps out all floats.
% %\end{document} % Floats are things like tables and figures.

%\clearpage     % \clearpage ends the page, and also dumps out all floats.

% %===================== List of Symbols ======================
\newpage
\addcontentsline{toc}{section}{List of Symbols}

\begin{center}
    {\large \bf List of Symbols\\ \vskip 1em}
    \vskip 1em
\end{center}
\singlespace

\begin{table}[h]
    \begin{tabular}{lll}
        $\vec{f}_i^t$ & & Feature vector of track $i$ at time $t$. \\
        $V$ & & Set of discrete categories (cluster IDs). \\
        $U$ & & Number of categories.  \\
        $\Theta$ & & Model estimate for shadows. \\ 
        $sh$ & & Shadow. \\
        $obj$ & & Object. \\
        $L_i$ & & Log of the probability of a sequence $O_i$ given a trained HMM. \\
        $\vec{O_i}$ & & Observation sequence $i$. \\
        $T_i$ & & Number of observations in sequence $i$. \\
        $M_c$ & & HMM that models the sequences in cluster $c$. \\
        $p_c$ & & Optimal rejection threshold for cluster $c$. \\
        $N_c$ & & Number of deviant patterns allowed in cluster $c$. \\
        $z$ & & $z$-score. \\
        $\theta_z$ & & Global alarm threshold. \\
        
        
    \end{tabular}
\end{table}

% %===================== List of Acronyms ======================
\newpage
\addcontentsline{toc}{section}{List of Acronyms}

\begin{center}
    {\large \bf List of Acronyms\\ \vskip 1em}
    \vskip 1em
\end{center}

\singlespace

\begin{table}[h]
    \begin{tabular}{lll}
        CCTV   & & Closed-Circuit Television. \\
        MoG    & & Mixture of Gaussian. \\
        CCV    & & Color Coherence Vector. \\
        DNM    & & Deterministic Nonmodel-Based Shadow Detection. \\
        NCC    & & Normalized Cross-Correlation. \\
        ML     & & Maximum Likelihood. \\
        IML    & & Incremental Maximum Likelihood. \\
        EM     & & Expectation Maximization. \\  
        DBN    & & Dynamic Bayesian Network. \\
        $k$-NN & & $k$-Nearest Neighbors. \\
        SVM    & & Support Vector Machine. \\
        PCA    & & Principal Component Analysis. \\
        MDL    & & Minimum Description Length. \\
        GMM    & & Gaussian Mixture Model. \\
        HMM    & & Hidden Markov Model. \\
        DTW    & & Dynamic Time Warping. \\ 
        LRT    & & Likelihood Ratio Test. \\
        ROC    & & Receiver Operating Characteristic. \\
        EER    & & Equal Error Rate.
    \end{tabular}
\end{table}

\newpage

\begin{table}[h]
    \begin{tabular}{lll}
        TP     & & Number of True Positives. \\ 
        FP     & & Number of False Positives. \\
        TN     & & Number of True Negatives. \\ 
        FN     & & Number of False Negatives. \\
        TPR    & & True Positive Rate. \\ 
        FPR    & & False Positive Rate. 
    \end{tabular}
\end{table}

\setlength{\parskip}{12pt}

