\setlength{\footskip}{8mm}
\chapter{Introduction} \label{introduction}
\label{sec:Introduction}

\section{Background} 
Roads accidents is a major problem in Thailand. Every year more than ten
thousands people die due to accidents on the road. The majors reasons being
excessive speeding, over taking too close, driving while drunk and drowsiness
while driving. All of these reasons are due to human cause. Being able to 
detect road lanes can lead to development of system that provides assistance to 
the driver. For example alerting the driver when their making lane change. Not 
only can it be used to develop system for providing drivers assistance it can 
also be used to ensure that the driver is driving safely. This might not be a 
system that every driver would like to install in their car but it would prove 
very beneficial to public transportation vehicles where the authorities can know 
if their employee are driving safely or not. 

Apart from drivers assistance system that can help reduce traffic accidents. 
Systems for enforcing traffic rules are also of interest to the police. 
Having police everywhere to make sure that traffic laws are being enforced isn't very practical. Thus camera can be installed to track traffic violations. 

\section{Problem Statement}
Detecting road lanes is the most important step in any lane tracking 
application. For example a lane departure warning system depends on the accuracy 
of the lane boundary in order to estimate the vehicle position from the lane. 
Another application that can be used for traffic enforcement is to detect 
vehicles that are changing lanes at curves. 

\section{Objectives}
\begin{enumerate} 
  \item Design and implement a system to detect road lanes with a camera mounted in front of the car. 
  \item Design and implement a system to detect road lanes with a camera mounted at the side of the road. 
  \item Design and implement a system to track the road lanes over a period of time. 
  \item Perform an evaluation for the designed system to ensure the system accuracy. 
\end{enumerate}

\section{Assumptions and Limitations}
\begin{enumerate}
\item Since most accidents occur on big roads such as highway, this thesis will
focus on detecting road lanes on highway where the width of the lane marking is
known.
\item The system will be dependent on the camera used and the way the camera is
mounted; i.e. the intrinsic and extrinsic parameters of the camera must be
known prior to running the system.
\end{enumerate}

\section {Thesis Outline}
This thesis is organized as follow: 
\begin{enumerate}
  \item Chapter 2 describes the relevant literature and the algorithms that is related to this thesis. 
  \item Chapter 3 describes the algorithms used to implement the system. 
  \item Chapter 4 describes the results obtained from the designed system. 
  \item Chapter 5 provides the conclusion and future works. 
\end{enumerate}

